Fail Faster

### 2025-03-22 paper/paper.tex
cut at a title
multi

\section{\name{}}
\label{section:faster-generators}

@@

In muli-stage programming (also known more simply as staging), programs execute
in multiple stages, with each stage producing the code to be run
in the next. For the purposes of this paper, we will
consider two stages: namely compile time and run time. In our context, staged programs
execute once at compile time, which produces more code, which is then
compiled and run at run time.

>>>>

\section{How can I make my Generator Library Faster?}
\label{section:faster-generators}

@@

In multi-stage programming (also known more simply as staging), programs execute
in multiple stages, with each stage producing the code to be run
in the next. For the purposes of this paper, we will
consider two stages: namely compile time and run time. In our context, staged programs
execute once at compile time, which produces more code, which is then
compiled and run at run time.
